### 2022-11-14 NSF2022/Description/specificaim1v2.tex
fixed overhanging figure

\section{Proposed Research}
\label{sec:proposed-work}
This proposal is an outgrowth of the 
PIs' ongoing successful collaboration.
Building off complementary expertises,
the specific aims of this proposal are:
mathematical analysis and three-dimensional
membrane energies
(\S \ref{sec:specificaim1}: PI Ryham),
BIE implementation for large granule-number
and three-dimensional suspensions
(\S \ref{sec:specificaim2}: PI Quaife),
and kinetic theory
(\S \ref{sec:specificaim3}: PI Young).
\subsection{Specific Aim 1: Membrane vesicles as self-organized granules}
\label{sec:specificaim1}
We introduced \eqref{eq:RBT}--\eqref{eqn:stressbalance} to complement
existing methods for studing vesicles and bilayers. The simulation
results in (Figures~\ref{fig:JPv_linearshear} and~\ref{fig:JPv_rupture})
show that two-dimensional, granule-based vesicles replicate the
equilibria and hydrodynamics for continuous curves~\cite{FuQuRyYo22,
Fu2018_SIAM}. Our next goal is to study the model using rigorous
analysis and consider three-dimensionsional effects.

The first step is to obtain some solid well-posedness results for
\eqref{eq:RBT}--\eqref{eqn:stressbalance}. This system is an autonomous
ordinary differential equation for the body transformations $F_i$ with
the rate of change defined by a system of PDEs. Regarding the PDE system,
in the linear case and for fixed $t$, there is a
unique solution ($\phi, \uu$) under appropriate assumptions for the
boundaries and boundary data~\cite{manasthesis, rac-gre2016, LAX}. These
define instantaneous rigid body velocities and rotations,
leading to 
\begin{quotation}
  \noindent
  \textbf{Problem 1.} 
  Consider a collection of closed, disjoint granules $U_i$ with smooth
  boundary, with no-slip, rigid body motion boundary conditions, and a
  linear background flow. Assume a single-well potential and a smooth
  phase field boundary conditions. What is the well-posedness in time of
  the coupled system \eqref{eq:RBT}--\eqref{eqn:stressbalance}?
\end{quotation}
Problem 1 involves mathematically interesting techniques. First, we
must establish that the system has a local-in-time solution. This
involves domain perturbations and estimates for the solutions of second
order elliptic equations~\cite{Savar2002DomainPA, DANERS20081,
Lamboley2015EstimatesOF}, which also find extensive application in
extremal domain problems~\cite{Schiffer1954VariationOD,
Henrot2006ExtremumPF, bogosel:hal-03607776,Bogosel2022OnTP}, for
example. For global-in-time solutions, we can 
use lubrication forces~\cite{cawthorn_balmforth_2010, leal_2007}.
Here, the lubrication force required to bring granules into contact
blows up with distance, 
and we must analyze whether the attraction \eqref{eqn:stressbalance}
stays finite in order to  
guarantee positivity in the distance between granules.
Finally, we can study the granule-flow behavior in the zero-decay length
limit. This limit should recover the hydrodynamics of a (noninteracting)
rigid-body suspension.

In the double-well potential case, equation~\eqref{eqn:phase} is a
nonlinear Allen-Cahn equation. This situation models granules immersed
in a two-phase fluid (e.g.~granules in an emulsion) where there is an
interesting interplay between the long-range alignment of granules and
the diffusive interface energy of the free boundary between fluid
phases. On unbounded domains like $\Omega(t)$, Allen-Cahn equations can
have multiple solutions~\cite{Alama1997StationaryLS,
Alikakos2008OnAE, Bronsard1993OnTB, Byeon2014SolutionsOH, Byeon2013OnAP,
Alessio2005ENTIRESI, Trumper2007ExistenceOA, Benci2019MultipleSF} and so
we must reformulate~\eqref{eqn:phase}. An appropriate reformulation
is the following initial value problem with transport:
\begin{align}
  \label{eqn:phase_transport}
  \phi_t + \uu \cdot \nabla
  = -\beta \frac{\delta E}{\delta \phi}
  = \beta(\epsilon^2 \Delta \phi - W'(\phi)),
  \quad \phi(\xx,0) = \phi_0(\xx),
\end{align}
for initial data $\phi_0$. The modified system enjoys an energy law
similar to~\eqref{eq:energy_law} with an addtional dissipation term
involving the square the Euler-Lagrange derivative $\frac{\delta
E}{\delta \phi}$ and dampening factor $\beta > 0$. There are several
works dealing with the characterization of the geometric evolution of
interfaces under the Allen-Cahn and Cahn-Hilliard
equations~\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF,
Dai2019WeakSF, Promislow2017ExistenceBA, Dai2015CompetitiveGE,
Promislow2012CriticalPO, Dai2022GeometricEO, Dai2020MinimizersFT,
Dai2013GeometricEO, Promislow2022UndulatedBI} and well-posedness
results when coupled to flow in static domains~\cite{Jiang2017TwophaseIF,
Liu2012StrongSF, Giorgini2019WellPosednessOA, Wu2022WellposednessOA,
Gal2010AsymptoticBO, Giorgini2020DiffuseIM, Giorgini2019UniquenessAR}.
The proposed research extends these results to problems with moving
domains. A closely related and strongly developing direction in the area
of nematics liquid crystals concerns the interaction of Landau de Gennes
functionals with colloids, and studies the qualitative structure of
defects around single or multiple coloidal
particles~\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT,
Alama2021SaturnRD, PhysRevE.96.042702}. PI Ryham has several works on
membrane vesicles dealing both with Allen-Cahn formulations and
fluid-vesicle interactions~\cite{QiangDu09, RYHAM20112929, RyCoEi12,
Ryham2017OnTV}.

@@

\begin{wrapfigure}[11]{r}{0.5\textwidth}
  \vspace{-8pt}
  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:amphiphilic_assembly} \footnotesize
  Self-organization under amphiphilic boundary condition. (a) Granules
  first match hydrophobic tails (red), (b) then align length-wise. (c)
  The same pattern of self-organization holds in three dimensions, as
  simulated by Kohl, Corona, and
  Veerapaneni~\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}

@@

Tools for addressing Problem 2 have been developed for bulk nematic liquid
crystal potentials in the area of colloidal
homogenization~\cite{Canevari2019DesignOE, doi:10.1137/18M1163919,
  doi:10.1137/18M1163919, BERLYAND200597, doi:10.1137/130910348}, and
the problem is closely related to dimension reduction for curved nematics
confined to thin films~\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,
  doi:10.1142/S0218202516500470, FoFrLe07}.
PI Ryham has carried out sharp interface-limit analyses for phase field
formulations of elastic bending energy~\cite{0951-7715-18-3-016, Du05},
approximations of Gaussian curvature and the Euler characteristic in
phase field~\cite{DuEuler}, and vanishing Debye-length in 
Poisson-Boltzman equations~\cite{Lee2018, 1531-3492_2006_2_357}.

>>>>

\section{Proposed Research}
\label{sec:proposed-work}
This proposal is an outgrowth of the PIs' ongoing successful
collaboration. Building off complementary expertises, the specific aims
of this proposal are: mathematical analysis and three-dimensional
membrane energies (\S\ref{sec:specificaim1}: PI Ryham), BIE
implementation for large granule-number and three-dimensional
suspensions (\S\ref{sec:specificaim2}: PI Quaife), and kinetic theory
(\S\ref{sec:specificaim3}: PI Young).

\subsection{Specific Aim 1: Membrane vesicles as self-organized granules}
\label{sec:specificaim1}
We introduced~\eqref{eq:RBT}--\eqref{eqn:stressbalance} to complement
existing methods for studing vesicles and bilayers. The simulation
results in Figures~\ref{fig:JPv_linearshear} and~\ref{fig:JPv_rupture}
show that two-dimensional, granule-based vesicles replicate the
equilibria and hydrodynamics for continuous curves~\cite{FuQuRyYo22,
Fu2018_SIAM}. Our next goal is to study the model using rigorous
analysis and consider three-dimensionsional effects.

The first step is to obtain some solid well-posedness results
for~\eqref{eq:RBT}--\eqref{eqn:stressbalance}. This system is an
autonomous ordinary differential equation for the body transformations
$\FF_i$ with the rate of change defined by a system of PDEs. Regarding
the PDE system, in the linear case and for fixed $t$, there is a unique
solution ($\phi, \uu$) under appropriate assumptions for the boundaries
and boundary data~\cite{manasthesis, rac-gre2016, LAX}. These define
instantaneous rigid body velocities and rotations, leading to the
following problem.
\begin{quotation}
  \noindent
  \textbf{Problem 1.} 
  Consider a collection of closed, disjoint granules $U_i$ with smooth
  boundary, with no-slip, rigid body motion boundary conditions, and a
  linear background flow. Assume a single-well potential and a smooth
  phase field boundary conditions. What is the well-posedness in time of
  the coupled system \eqref{eq:RBT}--\eqref{eqn:stressbalance}?
\end{quotation}
Problem 1 involves mathematically interesting techniques. First, we must
establish that the system has a local-in-time solution. This involves
domain perturbations and estimates for the solutions of second order
elliptic equations~\cite{Savar2002DomainPA, DANERS20081,
Lamboley2015EstimatesOF}, which also find extensive application in
extremal domain problems~\cite{Schiffer1954VariationOD,
Henrot2006ExtremumPF, bogosel:hal-03607776,Bogosel2022OnTP}, for
example. For global-in-time solutions, we can use lubrication
forces~\cite{cawthorn_balmforth_2010, leal_2007}. Here, the lubrication
force required to bring granules into contact blows up with distance,
and we must analyze whether the attraction~\eqref{eqn:stressbalance}
stays finite in order to guarantee positivity in the distance between
granules. Finally, we can study the granule-flow behavior in the
zero-decay length limit. This limit should recover the hydrodynamics of
a (noninteracting) rigid-body suspension.

\begin{wrapfigure}[11]{r}{0.5\textwidth}
  \vspace{-8pt}
  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:amphiphilic_assembly} \footnotesize
  Self-organization under amphiphilic boundary condition. (a) Granules
  first match hydrophobic tails (red), (b) then align length-wise. (c)
  The same pattern of self-organization holds in three dimensions, as
  simulated by Kohl, Corona, and
  Veerapaneni~\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
In the double-well potential case, equation~\eqref{eqn:phase} is a
nonlinear Allen-Cahn equation. This situation models granules immersed
in a two-phase fluid (e.g., granules in an emulsion) where there is an
interesting interplay between the long-range alignment of granules and
the diffusive interface energy of the free boundary between fluid
phases. On unbounded domains like $\Omega(t)$, Allen-Cahn equations can
have multiple solutions~\cite{Alama1997StationaryLS,
Alikakos2008OnAE, Bronsard1993OnTB, Byeon2014SolutionsOH, Byeon2013OnAP,
Alessio2005ENTIRESI, Trumper2007ExistenceOA, Benci2019MultipleSF} and so
we must reformulate~\eqref{eqn:phase}. An appropriate reformulation
is the following initial value problem with transport:
\begin{align}
  \label{eqn:phase_transport}
  \phi_t + \uu \cdot \nabla
  = -\beta \frac{\delta E}{\delta \phi}
  = \beta(\epsilon^2 \Delta \phi - W'(\phi)),
  \quad \phi(\xx,0) = \phi_0(\xx),
\end{align}
for initial data $\phi_0$. The modified system enjoys an energy law
similar to~\eqref{eq:energy_law} with an addtional dissipation term
involving the square the Euler-Lagrange derivative $\frac{\delta
E}{\delta \phi}$ and dampening factor $\beta > 0$. There are several
works dealing with the characterization of the geometric evolution of
interfaces under the Allen-Cahn and Cahn-Hilliard
equations~\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF,
Dai2019WeakSF, Promislow2017ExistenceBA, Dai2015CompetitiveGE,
Promislow2012CriticalPO, Dai2022GeometricEO, Dai2020MinimizersFT,
Dai2013GeometricEO, Promislow2022UndulatedBI} and well-posedness
results when coupled to flow in static domains~\cite{Jiang2017TwophaseIF,
Liu2012StrongSF, Giorgini2019WellPosednessOA, Wu2022WellposednessOA,
Gal2010AsymptoticBO, Giorgini2020DiffuseIM, Giorgini2019UniquenessAR}.
The proposed research extends these results to problems with moving
domains. A closely related and strongly developing direction in the area
of nematics liquid crystals concerns the interaction of Landau de Gennes
functionals with colloids, and studies the qualitative structure of
defects around single or multiple coloidal
particles~\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT,
Alama2021SaturnRD, PhysRevE.96.042702}. PI Ryham has several works on
membrane vesicles dealing both with Allen-Cahn formulations and
fluid-vesicle interactions~\cite{QiangDu09, RYHAM20112929, RyCoEi12,
Ryham2017OnTV}.

@@

@@

Tools for addressing Problem 2 have been developed for bulk nematic
liquid crystal potentials in the area of colloidal
homogenization~\cite{Canevari2019DesignOE, doi:10.1137/18M1163919,
BERLYAND200597, doi:10.1137/130910348}, and the problem is closely
related to dimension reduction for curved nematics confined to thin
films~\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,
doi:10.1142/S0218202516500470, FoFrLe07}.  PI Ryham has carried out
sharp interface-limit analyses for phase field formulations of elastic
bending energy~\cite{0951-7715-18-3-016, Du05}, approximations of
Gaussian curvature and the Euler characteristic in phase
field~\cite{DuEuler}, and vanishing Debye-length in Poisson-Boltzman
equations~\cite{Lee2018, 1531-3492_2006_2_357}.
